Simplifying Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-05-16 article.rnw
Add a missing semantic newline.
Change "regularising" to "simplifying" in the title.
"Regularising" is a word that needs explanation, but an explanation
does not fit neatly anywhere in the paper.
Fix the format of subreferences within figure captions.
(a) rather than "fig. 1a".
Unfortunately, this has necessitated a change from \cref to \subref.

@@

%Title Page
% DBS: What about "Simplifying Lotka--Volterra interaction matrices by species grouping", with or without the bit after the colon (and where I lean slightly in favor of the "with" option)
\title{Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable} %TODO: Remove the word "regularising" from the title.
\author{Christopher R.\ P.\ Brown}
\author{Daniel B.\ Stouffer}
\affil{Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Christchurch, New Zealand}
\date{}

@@

	\caption{%
		The groupings and competition coefficients of a grouped Lotka--Volterra model fitted to the six studied \emph{Drosophila} species.
		This represents the single model with the best {\ic} (\probnum{\Sexpr{brute_data$statistics[best_model_index,ic]}}). %TODO: Debug this.
		\Cref{fig:best-alpha-matrix} shows the competition coefficients, where a competition coefficient in a block represents the same coefficient being used for multiple interactions, per the groupings.
		\Cref{fig:best-coclassification-cols} and \cref{fig:best-coclassification-rows} show the coclassification matrices derived from the groupings of the columns and rows respectively.
		These coclassification matrices are averaged for all models, weighted by Akaike weights, to produce \cref{fig:coclassification}.
		Species have been reordered that species which are grouped together appear adjacent.
		The ordering is the same in \cref{fig:best-coclassification-cols} and \cref{fig:best-coclassification-rows} as shown in \cref{fig:best-alpha-matrix}.
	}
	\label{fig:best-model}
\end{figure}

@@

	\caption{%
		Coclassification matrices of the Lotka--Volterra competitive effects and responses of the six studied \emph{Drosophila} species, weighted by Akaike weights.
		The cell for a pair of species represents the probability that the best grouping, as determined by the Akaike weights of the grouped models, places those two species in the same group.
		\Cref{fig:coclassification-cols} represents the grouping of species' competitive effects upon other species (columns of the interaction matrix), while \cref{fig:coclassification-rows} represents the grouping of species' responses to competition (rows of the interaction matrix).
	}
	\label{fig:coclassification}
\end{figure}

% DBS: Within the caption, the reference to a subfigure should just be (a) and (b), not Figure 2a and fig. 2b.

>>>>

\captionsetup{subrefformat=parens} %Changes only \subref, not \ref.
\let\Subref\subref
%TODO: Make \cref figure out if it should be a subref, and use cref throughout.

@@

%Title Page
\title{Simplifying Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable}
\author{Christopher R.\ P.\ Brown}
\author{Daniel B.\ Stouffer}
\affil{Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Christchurch, New Zealand}
\date{}

@@

	\caption{%
		The groupings and competition coefficients of a grouped Lotka--Volterra model fitted to the six studied \emph{Drosophila} species.
		This represents the single model with the best {\ic} (\probnum{\Sexpr{brute_data$statistics[best_model_index,ic]}}). %TODO: Debug this.
		\Subref{fig:best-alpha-matrix} shows the competition coefficients, where a competition coefficient in a block represents the same coefficient being used for multiple interactions, per the groupings.
		\Subref{fig:best-coclassification-cols} and \subref{fig:best-coclassification-rows} show the coclassification matrices derived from the groupings of the columns and rows respectively.
		These coclassification matrices are averaged for all models, weighted by Akaike weights, to produce \cref{fig:coclassification}.
		Species have been reordered that species which are grouped together appear adjacent.
		The ordering is the same in \subref{fig:best-coclassification-cols} and \subref{fig:best-coclassification-rows} as shown in \subref{fig:best-alpha-matrix}.
	}
	\label{fig:best-model}
\end{figure}

@@

	\caption{%
		Coclassification matrices of the Lotka--Volterra competitive effects and responses of the six studied \emph{Drosophila} species, weighted by Akaike weights.
		The cell for a pair of species represents the probability that the best grouping, as determined by the Akaike weights of the grouped models, places those two species in the same group.
		\Subref{fig:coclassification-cols} represents the grouping of species' competitive effects upon other species (columns of the interaction matrix), while \subref{fig:coclassification-rows} represents the grouping of species' responses to competition (rows of the interaction matrix).
	}
	\label{fig:coclassification}
\end{figure}
